\documentclass{homework}
\author{Danbo CHEN}
\class{EDUTL 5902: Advanced Academic Writing for
Multilingual Graduate Students}
\date{\today}
\title{Academic Integrity and Academic Misconduct}
%\address{Bayt El-Hikmah}

%\graphicspath{{./media/}}

\begin{document} \maketitle

\question Paraphrase the following passage. Technical or specialized terms which should not be changed are underlined:

We assessed the prevalence of IgG, IgA, and IgM antibodies recognizing the SARS-CoV-2 full-length nucleocapsid protein (NC) or spike receptor-binding domain (RBD) in serum samples from 132 infected patients.

\begin{sol}

We evaluated the presence of immunoglobulin G (IgG), immunoglobulin A (IgA), and immunoglobulin M (IgM) targeting the full-length nucleocapsid protein (NC) or spike receptor-binding domain (RBD) of SARS-CoV-2 in serum samples collected from 132 infected individuals.

  
\end{sol}

\question Paraphrase the following passage. Technical or specialized terms which should not  be changed are  underlined :

Individual reading passages were used during baseline, intervention, and probe sessions. Reading passages utilized in this study were found on an educational website (Education.com) which offered educational tools and learning resources for parents and educators with lessons ranging from pre-kindergarten through high school.

\begin{sol}

Individual reading passages were employed during baseline, intervention, and probe sessions. These reading materials were sourced from an educational website (Education.com) that provides parents and educators with various learning tools and resources, including lessons spanning from pre-kindergarten to high school.

\end{sol}

% \question What are some of the obvious cases of Misconduct?

% \begin{sol}
% \begin{itemize}
%     \item Violation of Course Rules: Breaking rules specified for a class or assignment.
%     \item Possession of Unauthorized Materials: Using unapproved resources during exams or assignments.
%     \item Plagiarism: Submitting work that is not one’s own or copying others' work without proper credit.
%     \item Falsification of Data: Submitting fake or altered data for assignments or research.
%     \item Substituting Students: Having someone else take an exam or complete assignments.
%     \item Grade Alteration: Changing grades or tampering with academic records.
% \end{itemize}

  % \img<wheel>[0.26]{Cipher wheels.}{cipher.png, diagram.jpg}

  % The Python program is given in listing \ref{cpr} and the encryption is given in table \ref{enc}.

  % \lstinputlisting[language=Python, caption={Python 3 implementing figure \ref{wheel} left wheel.}, label=cpr]{code/prog.py}

  % \tbl<enc>{Caesar cipher} {
  %   Plain Text  & FOUR & SCORE & AND & SEVEN & YEARS & AGO \\
  %   Cipher Text & KTZW & XHTWJ & FSI & XJAJS & DJFWX & FLT \\
  % }
% \end{sol}

% \question List and briefly describe the “Ten Suggestions for Preserving Academic Integrity”.

% \begin{sol}
% \begin{enumerate}[label=\arabic*.]
%     \item Familiarize yourself with course-specific guidelines and follow them strictly.
%     \item Properly cite all sources to avoid plagiarism.
%     \item Work on assignments and exams individually unless collaboration is explicitly allowed.
%     \item Do not use unauthorized aids or materials during exams or assignments.
%     \item Only use materials and references approved by the instructor.
%     \item Submit work that reflects your own effort and understanding.
%     \item Avoid fabricating, falsifying, or misrepresenting research data.
%     \item Inform relevant authorities if you observe academic misconduct.
%     \item Avoid last-minute work to reduce the temptation to cheat.
%     \item Ask your instructor or teaching assistant if you are unsure about academic integrity expectations.
% \end{enumerate}
% \end{sol}
% % citations

\begin{thebibliography}{9}

\bibitem{1}
% Ohio State University. (n.d.). \textit{Defining Academic Misconduct and Academic Integrity}. Retrieved from \url{https://www.osu.edu}
Southward, J., Goo, M. (2019). \textit{Repeated reading as an intervention for high school students identified with a specific learning disability}. International Journal of Special Education, 34(1), 255–270.
\bibitem{2}
Sterlin, D., Mathian, A., Miyara, M., Mohr, A., Anna, F., Claër, L., \& Gorochov, G. (2021). \textit{IgA dominates the early neutralizing antibody response to SARS-CoV-2}. Science translational medicine, 13(577).
\end{thebibliography}

% \bibliographystyle{plain}
% \bibliography{citations}

\end{document}
